Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-12 Ben_Manuscripts/structure_paper/Draft.tex
draft updates

%\makeatletter
%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
%  \typeout{(#1)}
%  \@addtofilelist{#1}
%  \IfFileExists{#1}{}{\typeout{No file #1.}}
%}
%\makeatother
% 
%\newcommand*{\myexternaldocument}[1]{%
%    \externaldocument{#1}%
%    \addFileDependency{#1.tex}%
%    \addFileDependency{#1.aux}%
%}

@@

  Nanostructured porous membranes made from the cross-linked hexagonal phase of
  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
  selective separations.  In this work, we develop an atomistic molecular model
  of an LLC membrane. We show that our model is maximally consistent with
  experimental observations by comparing simulated X-ray Diffraction (XRD)
  patterns and calculated ionic conductivity to their experimental counterparts.
  We explore, in depth, the composition and structure of the nanopores in order
  to give insights that are not easily accessible to experimentalists.  The
  clearer picture of the nanoscopic structure of these membranes provided in this
  study will enable a better understanding of the mechanisms of small molecule
  transport within these nanopores.
  %MRS7: some more of the conclusions should be in the abstract.  'introduction' just raises questions, but 
  %'abstract' should give a executive-level summary of the answers.
  \end{abstract}

@@

  %MRS: abstract seems a bit limited, describe more generally (and
  briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  It seems out of balance to be talking about only one application.

@@

  The feasibility of LLC membranes has been demonstrated using LLCs that form
  the type 1 bicontinuous cubic (Q\textsubscript{I})
  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases (See Figure~\ref{fig:bcc_v_hII}). When separating organic solutes from
  NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
  selectivity 2--3 times higher than commercial RO and 6--12 times higher than
  commercial NF membranes \cite{dischinger_application_2017}.  When separating a
  series of various sized dyes, the H\textsubscript{II} phase membrane showed
  complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.

  The H\textsubscript{II} phase pore geometry is has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). The most
  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

  % BJC: I like this figure, but I don't know if it is necessary in the main body. i  % Maybe move to supplemental. Thoughts?
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
        \centering
        \includegraphics[trim=-2cm 0 0 0, clip, height=4.5cm]{Dibrpyr14.eps}
        \includegraphics[height=4.5cm]{bcc_phases.png}
        \caption{}\label{fig:bcc_phases}
  \end{subfigure}
  \hspace{1cm}
  \begin{subfigure}{0.45\textwidth}
        \centering
        \includegraphics[trim=0 -0.5cm 0 -0.5cm, clip, height=4.5cm]{NaGA3C11.eps}
        \includegraphics[height=4.5cm]{hexagonal_packing.png}
        \caption{}\label{fig:hII_phase}
  \end{subfigure}
%MRS5: not sure Q should be in here.  Could cut length by removing some of the detail about Q phase, since it 
isn't discussed in the paper. 
  \caption{The choice of LLC monomer and solvent leads to different accessible liquid
        crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
        in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
        represent the interface between the hydrophilic and hydrophobic regions of the unit
        cell. 
        %MRS7: not needed
        %As pictured, we assume that each region occupies an equal volume. 
        The
        monomer shown in (b) will form the hexagonal columnar phase
        (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
         water is present) The blue region represent the hydrophilic pores while the cyan region represents the surrounding hydrophobic monomer tails.}\label{fig:bcc_v_hII}
  \end{figure}

@@

%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
  In 2016, Feng et al. showed that one could obtain the same result using a second
  technique termed soft confinement\cite{feng_thin_2016}. Current efforts are focused
  on extending the method to the H\textsubscript{II} phase and characterizing the 
  performance of these newly aligned systems.

@@

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    %MRS7: Adjusted the phrasing
    \caption{(a) Previous understanding of the pores are essentially speculations based on limited chemical and experimental data. (b) We use a detailed molecular model in this paper in order to appropriately model the pore's
      complex architecture which is crucial to understanding the mechanism of solute
	  transport. In both pictures, the head group region is colored blue and the tail region is
	  colored cyan. 
          %MRS7: don't think this is needed.
          %This image was generated from the molecular simulations run for this paper.
          }~\label{fig:detail}
  \end{figure}

  %Here 
  In this paper,
   we develop a molecular model of the Col\textsubscript{h} assembly formed by
  Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which will allow us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. We will use this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

@@

        %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
        % in many liquid crystal systems?
 	We are careful to avoid the term 'layers' since a liquid crystalline system has, by 
 	definition, long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
        %MRS7: look carefully at tenses.  Don't describe the research in future tense. 
        % if it's describing your presentation of the research in the paper , use present tense. 
        % If it's describing something you did, use past tense. I changed some of them, but not all.
 	%We will use 
        In this study, we use
        our atomistic molecular model to study how the system's structure is 
        affected
 	%effected 
        by the density of monomers surrounding each pore's hydrophilic core.

@@

	On the short timescales accessible to MD
        %MRS7: added the following to make it clear the scale of the effort
        (even the 100's of nanoseconds of simulation peformed here are short compared to experimental timescales),
        we observe distinct metastable configurations
	which depend on starting configuration. We simulated XRD patterns of our system and 
	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
	model creates a nanoscopic chemical environment maximally consistent with experiment within 
	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
	interpretations	of the WAXS pattern and refute others.

@@

  Using equilibrated structures, we carry out various calculations to
  characterize the system. We define the point at which a system is equilibrated
  based on when the distance between pores stops changing.  We determined when
  the distances stopped changing by applying the statistical test,
  \texttt{pymbar.timeseries.detectEquilibration}, to the time series
  \cite{chodera_simple_2016,shirts_statistically_2008}. Simulations of 400 ns
  %MRS7: is there a typical total time as well?
  give at least 50 ns of equilibrated simulation trajectory.

@@

  \subsubsection{\textit{Simulated structure factor calculations}}

@@

  We calculated ionic conductivity using two different methods for robustness.
  The Nernst-Einstein relation, relates the DC ionic conductivity, $\sigma$, to ion
  diffusivity, $D$, concentration, $C$, ion charge, $q$, the Boltzmann constant,
  $k_b$, and temperature, $T$: 
  \begin{equation}
	\sigma = \dfrac{q^2CD}{k_b T} 
	\label{eqn:nernst_einstein}
  \end{equation}
  We measured sodium ion diffusion coefficients by calculating the slope
  of the linear region of the z-direction mean square displacement curve as
  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
  visualized the MSD plot to determine where to begin and end a linear fit. We
  measured ion concentration with respect to the volume of the entire unit cell. 
  The second method, termed the Collective Diffusion model, measures the
  movement of the collective variable, Q, which is defined as the amount of
  charge transfer through the system and can be thought to represent the center
  of charge of the system. The conductance, $\gamma$, of the system can be
  calculated as:
  \begin{equation}
	 \gamma = \dfrac{D_Q}{k_b T} 
	\label{eqn:collective_diffusion}
  \end{equation}
  We convert the resulting value to ionic conductivity by multiplying by
  channel length and dividing by the membrane cross sectional area. $D_Q$ is the
  diffusion coefficient of the collective variable Q. It is calculated using the
  Einstein relation. One can access a detailed derivation of the model elsewhere
  \cite{liu_collective_2013}.

@@

  %In order to fully match synthetic procedures, 
  In order to maximally match the experimental membrane synthesis process
  we created a cross-linking
  algorithm that one can apply to equilibrated structures. 
  %MRS7: I think the main purpose of crosslinking is mechanical stability.
  The purpose of
  cross-linking is to maintain macroscopic alignment of the crystalline domains,
  ensuring aligned, hexagonally packed pores. For that reason, we are not
  concerned with replicating the kinetics of the reaction, but instead emphasize
  %MRS7: Since the initial structure isn't that well captured by experiment, then it's probably
  % better to say that we are interested in knowing how much and in why way cross-linking modulates the structure. 
  the consistency of the final structure with experimental structural data.

@@

  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question \ref{point:monomernum}, we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
  of the supporting info for more details on sensitivity to initial layer spacing). 
  The pore-to-pore spacing was considered equilibrated, as defined in section~\ref{method:equil_time},
  % BJC5: this achemso format does not have section numbers so I can't reference sections
  % within this document.
  in all systems after 400 ns of simulation. Figure~\ref{fig:p2p} shows the equilibrated
  pore-to-pore distances for all systems tested.

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will in theory converge to
  a single equilibrium configuration, but that time is far beyond the 100's of nanosecond simulated here. 
  For simplicity, we 
  %MRS7: tenses
  %will group the systems studied here into
  the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
  ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
  The reason for these names will become clearer as we progress through our analysis.
  %MRS7: maybe above say where (i.e. what section) it will become clear?  Or possibly describe them here by order parameter instead of by starting distance, and state the correlation between starting distance and order parameter.
%    All systems tested are at least metastable on the timescales studied here, however not all 
%  make physical sense or fit the experimental profile that we are trying to match. In the limit
%  of infinite simulation time, all simulations will converge to a single density. It is our 
%  intention to choose an initial configuration which quickly reaches a monomer density close 
%  to experiment. We believe systems built with 5 columns per pore achieve this goal.

@@

  % BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
  to sample enough 
  truly
 independent configurations. 
 %MRS7: two things going on - they are not smooth because of lack of sampling WITHIN the metastable basin (somewhere in there mention angle averaging leads to less data at q=0 than anywhere else, but this is separate from being truly independent, which would mean totally converged in the equilibrium ensemble (i.e. reaching a single equilibrium ensemble in the >miliseconds timescale)  Increasing the number of trajectory frames
  used to simulate the structure factor within a given interval of time does not offer 
  any improvement.
%MRS7: not sure what you mean above. Increasing the frequency of frames used? 
  %BJC5: put figure letters in upper left hand corner of each pattern.
  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			        %\caption{Sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
	        		%\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
	        		%\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			        %\caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
			\end{subfigure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore 
  the 
  %MRS7: possible or likely origin
  origin of each experimental reflection and form structural
  hypotheses related to their appearance in our simulated patterns. Specifically, we want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
  The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still
  not present. We will use 
  %MRS7: be more specific when you say ``this configuration'' Just the simulation at 280K? The system is a set of configuraitons. 
this configuration to more thoroughly explore the origin of R-spots.

@@

  In general, the composition of each region, particulary the pore region, is 
  similar between all systems. We believe we can solvate and study transport in any
  of the systems presented here and extract similar transport mechanisms. We will 
  need to verify that this assumption is true.

>>>>

@@

  Nanostructured porous membranes made from the cross-linked hexagonal phase of
  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
  selective separations. In this work, we develop an atomistic molecular model
  of an experimentally characterized LLC membrane. While it is relatively 
  straightforward to create a stable hexagonal phase model, we demonstrate that 
  closely reproducing the experimental pore structure requires a carefully 
  constructed initial configuration in order to avoid falling into a metastable
  basin. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
  maximum consistency between our structures and experiment. We show that pores 
  are likely composed of 5 columns of stacked LLC monomers which surround each
  hydrophilic core. Although this system has been reported as dry, we show that
  small amounts of water are necessary to fully reproduce the experimental XRD
  pattern due to asymmetries introduced by hydrogen bonds between monomer head
  groups and water molecules. We explore, in depth, the composition and 
  structure of the nanopores and reveal that there exists a composition gradient
  rather than a hard partition between the hydrophilic and hydrophobic regions.
  The clearer picture of the nanoscopic structure of these membranes provided in
  this study will enable a better understanding of the mechanisms of small 
  molecule transport within these nanopores.

  \end{abstract}

@@

  % MRS: abstract seems a bit limited, describe more generally (and
  % briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  
  % It seems out of       balance to be talking about only one application.

@@

  The feasibility of nanostructured LLC membranes for selective separations has been
  demonstrated using LLCs that form the type 1 bicontinuous cubic (Q\textsubscript{I})
  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases (See Figure~\ref{fig:bcc_v_hII}). When separating organic solutes from
  NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
  selectivity 2--3 times higher than commercial RO and 6--12 times higher than
  commercial NF membranes \cite{dischinger_application_2017}.  When separating a
  series of various sized dyes, the H\textsubscript{II} phase membrane showed
  complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.

  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

%  % BJC: I like this figure, but I don't know if it is necessary in the main body. i  % Maybe move to supplemental. Thoughts?
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%        \centering
%        \includegraphics[trim=-2cm 0 0 0, clip, height=4.5cm]{Dibrpyr14.eps}
%        \includegraphics[height=4.5cm]{bcc_phases.png}
%        \caption{}\label{fig:bcc_phases}
%  \end{subfigure}
%  \hspace{1cm}
%  \begin{subfigure}{0.45\textwidth}
%        \centering
%        \includegraphics[trim=0 -0.5cm 0 -0.5cm, clip, height=4.5cm]{NaGA3C11.eps}
%        \includegraphics[height=4.5cm]{hexagonal_packing.png}
%        \caption{}\label{fig:hII_phase}
%  \end{subfigure}
%%MRS5: not sure Q should be in here.  Could cut length by removing some of the detail about Q phase, since it 
%%isn't discussed in the paper. 
%  \caption{The choice of LLC monomer and solvent leads to different accessible liquid
%        crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
%        in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
%        represent the interface between the hydrophilic and hydrophobic regions of the unit
%        cell. 
%        %MRS7: not needed
%        %As pictured, we assume that each region occupies an equal volume. 
%        The
%        monomer shown in (b) will form the hexagonal columnar phase
%        (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
%         water is present) The blue region represent the hydrophilic pores while the cyan region represents the surrounding hydrophobic monomer tails.}\label{fig:bcc_v_hII}
%  \end{figure}

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
  In 2016, Feng et al. showed that one could obtain the same result using a second
  technique termed soft confinement\cite{feng_thin_2016}. Current efforts are focused
  on extending the method to the H\textsubscript{II} phase and characterizing the 
  performance of these newly aligned systems.

@@

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use a detailed molecular 
    model in this paper in order to appropriately model the pore's complex architecture
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

  In this paper, we develop a molecular model of the Col\textsubscript{h} assembly 
  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which will allow us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. We will use this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

@@

    %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
    % in many liquid crystal systems?
    %BJC5: changed to 'many liquid crystalline systems'
 	We are careful to avoid the term 'layers' since many liquid crystalline systems
 	have long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
    %MRS7: look carefully at tenses.  Don't describe the research in future tense. 
    % if it's describing your presentation of the research in the paper , use present tense. 
    % If it's describing something you did, use past tense. I changed some of them, but not all.
 	%We will use 
    In this study, we use our atomistic molecular model to study how the system's structure is 
    affected by the density of monomers surrounding each pore's hydrophilic core.

@@

	On the short timescales accessible to MD (even the 100's of nanoseconds of simulation 
	peformed here are short compared to experimental timescales), we observe distinct metastable
	configurations which depend on starting configuration. We simulated XRD patterns of our system and 
	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
	model creates a nanoscopic chemical environment maximally consistent with experiment within 
	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
	interpretations	of the WAXS pattern and refute others.

@@

  Using equilibrated structures, we carry out various calculations to
  characterize the system. We define the point at which a system is equilibrated
  based on when the distance between pores stops changing.  We determined when
  the distances stopped changing by applying the statistical test,
  \texttt{pymbar.timeseries.detectEquilibration}, to the time series
  \cite{chodera_simple_2016,shirts_statistically_2008}. Typically, the pore-to-pore
  distance equilibrates between 200 and 350 ns. We used data collected after 
  equilibration to do all subsequent analysis.

@@

  \subsubsection{\textit{Simulated structure factor calculations}}\label{method:xrd}

@@

  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
  temperature, $T$: 
  \begin{equation}
	\sigma = \dfrac{q^2CD}{k_b T} 
	\label{eqn:nernst_einstein}
  \end{equation}
  We measured sodium ion diffusion coefficients by calculating the slope
  of the linear region of the z-direction mean square displacement curve as
  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
  visualized the MSD plot to determine where to begin and end a linear fit. We
  measured ion concentration with respect to the volume of the entire unit cell.

@@

  In order to maximally match the experimental membrane synthesis process,
  we created a cross-linking algorithm that one can apply to equilibrated structures. 
  The primary purpose of cross-linking is to create a mechanically robust membrane.
  For that reason, we are not concerned with replicating the kinetics of the reaction, 
  but instead emphasize understanding how much and in what way cross-linking modulates
  the system's structure.

@@

  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question \ref{point:monomernum}, we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
  of the supporting info for more details on sensitivity to initial layer spacing). 
  We considered the pore-to-pore spacing to be equilibrated as defined in section~\ref{method:equil_time}.
  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested.

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will in theory converge to
  a single equilibrium configuration, but that time is far beyond the 100's of nanosecond simulated here. 
  For simplicity, we 
  %MRS7: tenses
  group the systems studied here into the ordered and disordered basins. Any system where 
  $\mathit{d}=3.7$ \AA~will be included in the
  ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
  The reason for these names will become clearer as we progress through our analysis.
  %MRS7: maybe above say where (i.e. what section) it will become clear?  Or possibly describe them here by order parameter instead of by starting distance, and state the correlation between starting distance and order parameter.
%    All systems tested are at least metastable on the timescales studied here, however not all 
%  make physical sense or fit the experimental profile that we are trying to match. In the limit
%  of infinite simulation time, all simulations will converge to a single density. It is our 
%  intention to choose an initial configuration which quickly reaches a monomer density close 
%  to experiment. We believe systems built with 5 columns per pore achieve this goal.

@@

  % BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the axis where $q_r$=0. There are
  two main reasons for this noise. First is that we angle averaged the 3D structure factor 
  (see section~\ref{method:xrd}) which inherently gives less data as q approaches 0. Second, 
  our simulations are not long enough to sample enough truly independent configurations within
  their respective metastable basins. By sampling more uncorrelated equilibrium configurations,
  we can suppress some of the noise (See section S\ref{S-section:xrd_noise}).
 %MRS7: two things going on - they are not smooth because of lack of sampling WITHIN the metastable basin (somewhere in there mention angle averaging leads to less data at q=0 than anywhere else, but this is separate from being truly independent, which would mean totally converged in the equilibrium ensemble (i.e. reaching a single equilibrium ensemble in the >miliseconds timescale)

%  Increasing the number of trajectory frames used to simulate the structure factor within
%  a given interval of time does not offer any improvement.
%MRS7: not sure what you mean above. Increasing the frequency of frames used? 
%BJC6: yes, since the frames are just more snapshots of non-independent configurations. I think this is already implied above.

  %BJC5: put figure letters in upper left hand corner of each pattern.
  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			        %\caption{Sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
	        		%\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
	        		%\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			        %\caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
			\end{subfigure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore the possible origin of each experimental reflection and form 
  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
  want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
  The relative intensity of R-spots is slightly higher than in experiment (1.5 vs. 1.3). R-double 
  is still not present. We will use the system simulated at 280K to more thoroughly explore the 
  origin of R-spots.

@@

  %BJC6: lead with this vvv
  In general, the composition of each region, particulary the pore region, is 
  similar between all systems. We believe we can solvate and study transport in any
  of the systems presented here and extract similar transport mechanisms. We will 
  need to verify that this assumption is true.
